D3064R0: How to Avoid OOTA Without Really Trying

### 2024-02-21 ootavacuous.tex
Alan Stern February 21 feedback, Section 8.3
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Where a C++ implementation's primary function is to correctly execute
a C++ program, the function of tooling is often to evaluate properties
of possible executions of that same program.
While implementations are never supposed to break a semantic dependency,
tools are in some cases permitted to misclassify them, as shown in
Table~\ref{tab:Semantic-Dependency Classification For Tools}.

>>>>

Where a C++ implementation's primary function is to correctly execute
a C++ program, the function of tooling is often to evaluate properties
of possible executions of that same program.
While implementations should avoid breaking semantic dependencies,
tools are in some cases permitted to misclassify them, as shown in
Table~\ref{tab:Semantic-Dependency Classification For Tools}.
